---
title: "Untitled"
author: "Logan Ossentjuk"
date: "11/16/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(modelsummary)
library(corrplot)
library(broom)
library(here)
```

### Read in slo_homes.csv

```{r}
homes <- read_csv(here("slo_homes.csv"))
```

### Create a subset with 4 cities 

Task: create a subset (called homes_subset) that only contains observations where the city is: 

- "San Luis Obispo"
- "Atascadero"
- "Arroyo Grande" 
- "Santa Maria-Orcutt"

```{r}
homes_subset <- homes %>%  
  filter(City %in% c("San Luis Obispo", "Atascadero", "Arroyo Grande", "Santa Maria-Orcutt" ))
```


### A little exploration 

Task: Create a summary table that has the mean and standard deviation of home prices grouped by city and sale status 

```{r, include = FALSE, eval = FALSE} 
#eval = FALSE makes the code chunk not run -> use that when doing exploratory analysis on a large data set 
homes_summary <- homes_subset %>% 
  group_by(City, Status) %>% 
  summarize(mean_price = mean(Price),
          sd_price = sd(Price))

homes_summary
```


Task: explore the relationship between square footage and home price. 

```{r}
ggplot(data = homes_subset, aes(x = SqFt, y = Price)) +
  geom_point(aes(color = City)) +
  geom_smooth(method = "lm")

```


### Try a fe linear models 

Use multiple linear regression to investigate relationships between several predictor variables and home price using `homes_subset`

Task: Create 2 different permutations of this model 

(1) Price - City, Bedrooms, Bathrooms, SqFt, Status (lm1)
(2) Price - City, SqFt, Status (lm2)
(3) Try another one (lm3)



```{r}
lm1 = lm(Price ~ City + Bedrooms + Bathrooms + SqFt + Status, data = homes_subset)
lm2 = lm(Price ~ City + SqFt + Status,  data = homes_subset)
lm3 = lm(Price ~ SqFt + Status, data = homes_subset)

# If I wanted San Luis Obispo to be the reference level: 
# Use fct_relevel to specify a new reference level 

new_homes_subset <- homes_subset %>%  #start with ohmes subset
  mutate(City = fct_relevel("San Luis Obispo")) #add a new column, create new version of City column that converts it to a factor and relevels San Luis Obispo as the reference level 

#This will use SLO as the reference level for city
lm_slo <- lm(Price ~ City + SqFt, data = new_homes_subset)

summary(lm_slo)

#54% of variance in sale price is explained by this model based on the R-Squared value 
```


### Explore correlations between quantitative variables 

Task: make a subset called homes_quant (starting from homes_subset) that only contains the variables from Price through SqFT

```{r}
homes_quant <- homes_subset %>% 
  select(Price:SqFt)

homes_cor <- cor(homes_quant)

corrplot(homes_cor, method = "ellipse")
```


### Compare AIC values

```{r}
AIC(lm1)
AIC(lm2)
```

### Use modelsummary() to return multiple model outputs 

```{r}
modelsummary(list(lm1, lm2, lm3))
```


### Check out diagnostic plots for lm1 

```{r}
plot(lm1)
```
### Use broom::augment() to return the prediction for existing observations

```{r}
homes_predictions <- augment(lm1)

#Make a histogram of the residuals from this model (lm1)
hist(homes_predictions$.resid)
ggplot(data = homes_predictions, x = .resid) +
  geom_histogram(bins = 30)
```

# BRANCHES ARE AWESOME